Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-11-28 paper_comparison/paper_comparison/paper_comparison.Rmd
update text

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with the $X_{raw}$ following a uniform distribution against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - F-test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residuals plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes noticeable.

The power of all four tests increases as the effect becomes larger. The power curve of F-test climbs aggressively from 25% to around 90% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect and remain lower than 25% throughout the period, showing that F-test is way more sensitive to the type of model defects that being considered. Meanwhile, the residuals plot

The power of visual test arises steadily to around 90% as $log_e(E)$ increases from 2 to 5, suggesting that the effect starts to make noticeable impact on the degree of the presence of the designed visual features. Other two inappropriate conventional tests shows improvement at the same time but at a lower rate. This coincides the point made by @cook1982residuals that residual-based tests for a specific type of model defect are sensitive to other types of model defects. At $log_e(E) \approx 6$, the power of both F-test and visual test reaches almost 100%. The power of Breusch--Pagan test and Shapiro--Wilk test reach around 75% and 30% respectively.

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with the $X_{raw}$ following a uniform distribution against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - F-test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residuals plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

In overall, the power of all four tests increases as the effect gets larger. The power curve of F-test climbs aggressively from 25% to around 90% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect and remain lower than 25% throughout the period, showing that F-test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residuals plots.

The power of visual test arises steadily to around 90% as $log_e(E)$ increases from 2 to 5, suggesting that the effect starts to make significant impact on the degree of the presence of the designed visual features. This can also be observed from the example residuals plots that when $log_e(E) = 2.5$, a weak "S-shape" starts to present. And as $log_e(E)$ increases, the visual pattern becomes much clearer. Other two inappropriate conventional tests shows improvement at the same time but at a lower rate. This coincides the point made by @cook1982residuals that residual-based tests for a specific type of model defect are sensitive to other types of model defects.

At $log_e(E) \approx 6$, the power of both F-test and visual test reaches almost 100%. The power of Breusch--Pagan test and Shapiro--Wilk test reach around 75% and 30% respectively.

Similarly, Figure \ref{fig:heterpower} shows the power of BP test, visual test and two other

### 2022-11-28 paper_comparison/paper_comparison/paper_comparison.tex
update text

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with the \(X_{raw}\)
following a uniform distribution against the natural logarithm of the
effect \(log_e(E)\) with comparison to the power of an exact test -
F-test, and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. At the bottom of the figure
\ref{fig:polypower}, there are a sequence of example residuals plots
with increasing levels of \(log_e(E)\). Readers can evaluate them from
left to right and determine at which level the departure from a good
residual plot becomes noticeable.

The power of all four tests increases as the effect becomes larger. The
power curve of F-test climbs aggressively from 25\% to around 90\% as
\(log_e(E)\) increases from 0 to 2, while power of other tests respond
inactively to the change of effect and remain lower than 25\% throughout
the period, showing that F-test is way more sensitive to the type of
model defects that being considered. Meanwhile, the residuals plot

The power of visual test arises steadily to around 90\% as \(log_e(E)\)
increases from 2 to 5, suggesting that the effect starts to make
noticeable impact on the degree of the presence of the designed visual
features. Other two inappropriate conventional tests shows improvement
at the same time but at a lower rate. This coincides the point made by
\citet{cook1982residuals} that residual-based tests for a specific type
of model defect are sensitive to other types of model defects. At
\(log_e(E) \approx 6\), the power of both F-test and visual test reaches
almost 100\%. The power of Breusch--Pagan test and Shapiro--Wilk test
reach around 75\% and 30\% respectively.

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with the \(X_{raw}\)
following a uniform distribution against the natural logarithm of the
effect \(log_e(E)\) with comparison to the power of an exact test -
F-test, and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. At the bottom of the figure
\ref{fig:polypower}, there are a sequence of example residuals plots
with increasing levels of \(log_e(E)\). Readers can evaluate them from
left to right and determine at which level the departure from a good
residual plot becomes detectable.

In overall, the power of all four tests increases as the effect gets
larger. The power curve of F-test climbs aggressively from 25\% to
around 90\% as \(log_e(E)\) increases from 0 to 2, while power of other
tests respond inactively to the change of effect and remain lower than
25\% throughout the period, showing that F-test is way more sensitive to
the type of model defects that being considered. Meanwhile, no
noticeable visual features can be spotted from the example residuals
plots.

The power of visual test arises steadily to around 90\% as \(log_e(E)\)
increases from 2 to 5, suggesting that the effect starts to make
significant impact on the degree of the presence of the designed visual
features. This can also be observed from the example residuals plots
that when \(log_e(E) = 2.5\), a weak ``S-shape'' starts to present. And
as \(log_e(E)\) increases, the visual pattern becomes much clearer.
Other two inappropriate conventional tests shows improvement at the same
time but at a lower rate. This coincides the point made by
\citet{cook1982residuals} that residual-based tests for a specific type
of model defect are sensitive to other types of model defects.

At \(log_e(E) \approx 6\), the power of both F-test and visual test
reaches almost 100\%. The power of Breusch--Pagan test and Shapiro--Wilk
test reach around 75\% and 30\% respectively.

Similarly, Figure \ref{fig:heterpower} shows the power of BP test,
visual test and two other
